Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-01-06 doc/JFLA2022/Slides/Slides.tex
small correction in the slides

\definecolor{orange}{rgb}{1.0,0.6,0.0}
\definecolor{darkorange}{rgb}{0.7,0.25,0.0}
\definecolor{plugincolor}{rgb}{0.6,0.0,0.6}
\definecolor{mathcolor}{rgb}{0.0,0.0,0.6}
\definecolor{coqstylecolor}{rgb}{0.0,0.0,01.0}
\definecolor{lightblue}{rgb}{0.2,0.2,1.0}
\definecolor{metavarcolor}{rgb}{0.5,0.0,1.0}
\definecolor{darkgreen}{rgb}{0.1,0.7,0.1}
\definecolor{answercolor}{rgb}{.08,.15,.8}
\definecolor{normalcolor}{rgb}{0.0,0.0,0.0}
\definecolor{exbluecolor}{rgb}{0.1,0.1,0.9}
\definecolor{dontlookcolor}{rgb}{0.5,0.5,0.5}
\definecolor{termcolor}{rgb}{0.0,0.1,0.9}
\definecolor{lookcolor}{rgb}{0.5,0.1,0.0}
\definecolor{prooftermcolor}{rgb}{0.3,0.1,1.0}
\definecolor{typecolor}{rgb}{1.0,0.6,0.0}
\definecolor{taccolor}{rgb}{0.70,0.10,0.0}
\definecolor{pink}{rgb}{0.8,0.6,0.6}
\definecolor{darkmagenta}{rgb}{0.4,0.0,0.6}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}

\usepackage{tikz}
\usepackage{tikzsymbols}
\usepackage{pifont}
\usetikzlibrary{arrows}

@@

\usepackage[firstpage]{draftwatermark} 
\setbeamercolor{background canvas}{bg=}%transparent canvas

@@

  \begin{block}{}
    Using combinatorial lemmas by  K. \& S., we prove (by mutual  transfinite induction on \textcolor{mathcolor}{$\alpha$}):
    \begin{quote}
      \begin{itemize}
      \item \textcolor{mathcolor}{$H'_\alpha$} is strictly monotonous
      \item \textcolor{mathcolor}{$\forall i, i \leq H'_\alpha(i)$}
      \item   If \textcolor{mathcolor}{$\beta<\alpha$}, then \textcolor{mathcolor}{$H'_\alpha(i)>H'_\beta(i)$} for all but a finite number of $i$ (we say that \textcolor{mathcolor}{$H'_\alpha$}
        \emph{dominates} \textcolor{mathcolor}{$H_\beta$}).
      \end{itemize}
    \end{quote}

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}
  \begin{block}{Library on ordinals}
    There exist already \coq libraries which formalize ordinal numbers.
    \begin{itemize}
    \item \gaia (José Grimm) : Formalization of Bourbaki's Elements of Mathematics. {\color{lookcolor}\emph{This library uses an ordinal representation compatible with ours. It is  written in SSReflect/Mathcomp, and is also maintained in \community}.}
    \item A formalization by Minki Cho, using a different representation.
{\color{darkorange}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

  \begin{block}{Call to contributors }
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. Please contribute!
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)

>>>>

\definecolor{orange}{rgb}{1.0,0.6,0.0}
\definecolor{darkorange}{rgb}{0.7,0.25,0.0}
\definecolor{plugincolor}{rgb}{0.6,0.0,0.6}
\definecolor{mathcolor}{rgb}{0.0,0.0,0.6}
\definecolor{coqstylecolor}{rgb}{0.0,0.0,01.0}
\definecolor{lightblue}{rgb}{0.2,0.2,1.0}
\definecolor{metavarcolor}{rgb}{0.5,0.0,1.0}
\definecolor{darkgreen}{rgb}{0.1,0.7,0.1}
\definecolor{answercolor}{rgb}{.08,.15,.8}
\definecolor{normalcolor}{rgb}{0.0,0.0,0.0}
\definecolor{exbluecolor}{rgb}{0.1,0.1,0.9}
\definecolor{dontlookcolor}{rgb}{0.5,0.5,0.5}
\definecolor{termcolor}{rgb}{0.0,0.1,0.9}
\definecolor{lookcolor}{rgb}{0.5,0.1,0.0}
\definecolor{prooftermcolor}{rgb}{0.3,0.1,1.0}
\definecolor{typecolor}{rgb}{1.0,0.6,0.0}
\definecolor{taccolor}{rgb}{0.70,0.10,0.0}
\definecolor{pink}{rgb}{0.8,0.6,0.6}
\definecolor{darkmagenta}{rgb}{0.4,0.0,0.6}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.4,0.8}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usepackage{pifont}
\usetikzlibrary{arrows}

@@

%\usepackage[firstpage]{draftwatermark} 
\setbeamercolor{background canvas}{bg=}%transparent canvas

@@

  \begin{block}{}
    Using combinatorial lemmas by  K. \& S., we prove (by mutual  transfinite induction on \textcolor{mathcolor}{$\alpha$}):
    \begin{quote}
      \begin{itemize}
      \item \textcolor{mathcolor}{$H'_\alpha$} is strictly monotonous
      \item \textcolor{mathcolor}{$\forall i, i \leq H'_\alpha(i)$}
      \item   If \textcolor{mathcolor}{$\beta<\alpha$}, then \textcolor{mathcolor}{$H'_\beta(i)<H'_\alpha(i)$} for all but a finite number of $i$ (we say that \textcolor{mathcolor}{$H'_\alpha$}
        \emph{dominates} \textcolor{mathcolor}{$H_\beta$}).
      \end{itemize}
    \end{quote}

@@

\begin{frame}[fragile]
  \frametitle{Perspectives}
  \begin{block}{Library on ordinals}
    There exist already \coq libraries which formalize ordinal numbers.
    \begin{itemize}
    \item \gaia (José Grimm) : Formalization of Bourbaki's Elements of Mathematics. {\color{lookcolor}\emph{This library uses an ordinal representation compatible with ours (from the \textcolor{plugincolor}{Cantor} contrib) . It is  written in SSReflect/Mathcomp, and is also maintained in \community}.}
    \item A formalization by Minki Cho, using a different representation.
{\color{darkorange}
\begin{verbatim}
Inductive Ord.t :=
| Ord.build: 
    forall (A: Type), (A -> Ord.t) -> Ord.t.
\end{verbatim}
}  
    \end{itemize}

@@

  \begin{block}{Call to contributors }
  {\color{plugincolor}\Hydras} and  {\color{plugincolor}\community} are on GitHub. {\color{cyan}Please contribute, reuse!}
      \begin{itemize}
      \item New chapters
      \item Any correction or improvement (text and/or proofs)
